Roster Review

### 2019-04-11 rosterReview.Rmd
Some 2B/3B replacement research

rosters_with_adj_projections %>% 
  mutate(third_base = grepl('3B',display_position),
         second_base = grepl('2B',display_position),
         position_plot_display = case_when(
           third_base & second_base ~ 'Both',
           third_base ~ '3B',
           second_base ~ '2B',
           TRUE ~ "Other")) %>% 
  filter(!position_plot_display == 'Other') %>% 
  mutate(team = fct_relevel(team, "Plouffe There It Is!")) %>% 
  ggplot(aes(x=team,y=zar,color=position_plot_display)) +
  geom_point(aes(text=name_full)) +
  coord_flip() -> both

@@

# free agents?

@@

>>>>

rosters_with_adj_projections %>%
  filter(type == 'batter') %>% 
  mutate(third_base = grepl('3B',display_position),
         second_base = grepl('2B',display_position),
         position = case_when(
           third_base & second_base ~ 'Both',
           third_base ~ '3B',
           second_base ~ '2B',
           TRUE ~ "Other")) %>% 
  mutate(team = fct_relevel(team, "Plouffe There It Is!")) %>% 
  ggplot(aes(x=team,y=zar,color=position)) +
  geom_point(aes(text=name_full)) +
  coord_flip() -> both

@@

rosters_with_adj_projections %>% 
  filter(team == 'Free Agent', 
         grepl('2B|3B',display_position)) %>% 
  arrange(zar %>% desc) %>% 
  head(30) %>% 
  View()

#free agents missing display position - not getting free agents from Yahoo

@@

```{r}
proj_batter %>% 
  mutate(zar = if_else(type=="batter",
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"])) %>% 
  filter(grepl("Frazier|Voit|Bell|Bradley|Flores",Name)) %>% 
  arrange(zar %>% desc) %>% 
  select(Name, Team, zar, G:z_sum) %>% 
  View()
```
